CO Interlopers Eloping from [C~\textsc{ii}] Surveys

### 2019-04-07 paper/ms.tex
Fix S/N for auto-spectrum
Separate multi-field section

The Fisher matrix for our measurement is
\beq\label{eq:fisher}
F_{i,j} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l,l'\\l > l'}} \sum_{\substack{m,m'\\m > m'}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
\eeq
where $l$, $l'$, $m$, and $m'$ sum over all lines being considered. Note that
we can make the substitution
\begin{equation*}
\sum_{\substack{l,l'\\l > l'}} \rightarrow 
\frac{1}{2} \sum_{\substack{l,l'\\l \neq l'}}\text{,}
\end{equation*}
without changing the value of the Fisher matrix. Thus it will sometimes be
easier to compute
\beq\label{eq:fisher4}
F_{i,j} = 
\frac{1}{4} \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l,l'\\l \neq l'}} \sum_{\substack{m,m'\\m \neq m'}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{.}
\eeq
We also note that a perfect auto-spectrum measurement will have a limit to the
precision of a $B_i$ as
\beq\label{eq:Bi_auto_snr}
\text{S}/\text{N}(B_i) = \frac{B_i^2}{\sqrt{N_i}}\sqrt{V_k}\text{.}
\eeq
This will be useful to compare to the $\text{S}/\text{N}$ we will compute for
the multi-field approach.

>>>>

The Fisher matrix for our measurement is
\beq\label{eq:fisher}
F_{i,j} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l,l'\\l > l'}} \sum_{\substack{m,m'\\m > m'}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
\eeq
where $l$, $l'$, $m$, and $m'$ sum over all lines being considered. Note that
we can make the substitution
\begin{equation*}
\sum_{\substack{l,l'\\l > l'}} \rightarrow 
\frac{1}{2} \sum_{\substack{l,l'\\l \neq l'}}\text{,}
\end{equation*}
without changing the value of the Fisher matrix. Thus it will sometimes be
easier to compute
\beq\label{eq:fisher4}
F_{i,j} = 
\frac{1}{4} \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l,l'\\l \neq l'}} \sum_{\substack{m,m'\\m \neq m'}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{.}
\eeq
We also note that a perfect auto-spectrum measurement will have a limit to the
precision of a $B_i$ as
\beq\label{eq:Bi_auto_snr}
\text{S}/\text{N}(B_i) = \frac{B_i^2}{N_i}\sqrt{V_k}\text{.}
\eeq
This will be useful to compare to the $\text{S}/\text{N}$ we will compute for
the multi-field approach.

\section{Three Field Case} \label{sec:three_field}
We begin by considering the three field case. While numerically evaluating the
Fisher matrix is straightforward for any number of lines, it is tractable to
evaluate analytically in the three field case. Since the behavior of the
Fisher matrix in the multi-field case is driven largely by the best measured
line, we can understand the behavior of the general case by studying first the
three field case.
